---
title: "Final Prediction Model"
author: "by Kaiqiong Zhao"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: false
    number_sections: true
    toc_depth: 4
    keep_md: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 11, fig.height = 8) 
```


```{r, echo=FALSE, results='hide', fig.keep='none'}
library(pROC)
library('scales')
library(ggeffects)

source(file.path("~/scratch/GREENWOOD_SCRATCH/kaiqiong.zhao/Projects/Safiya-trend", "Scripts/packages.R"))
load("/mnt/GREENWOOD_JBOD1/GREENWOOD_SCRATCH/kaiqiong.zhao/Projects/Mohammed-NSQIP-split-test/Data/NSQIP_final.RData")

options(digits = 4, scipen = 2)
#trop <- RSkittleBrewer::RSkittleBrewer("trop")
trop <- c("darkorange", "dodgerblue", "hotpink"  ,  "limegreen" , "yellow")
```




# Final Prediction Model


The following 12 varialbes were used in our prediction model.

```{r}
covs_use <- c("Age","DIABETES","Elective_Surgery", "Hypertension_On_Medication","SEX"     , "SMOKing","Length_Of_Stay", "Major_Morbidity", "Disease","Resection", "Operative_Time"   , "ASA_Class"  ) 

covs_use
```



The model has the form

```{r}
fmla_19 <- All_Readmissions_Our_Outcome ~ ASA_Class + DIABETES +  
  Elective_Surgery +  Hypertension_On_Medication + 
  SEX + SMOKing +   Major_Morbidity + Disease + Resection + Age + Operative_Time + Length_Of_Stay  + I(Length_Of_Stay^2) + I(Operative_Time^2) +
  Age:Resection +Hypertension_On_Medication:Elective_Surgery +  Length_Of_Stay:Major_Morbidity+ Length_Of_Stay:Disease

fmla_19
```




```{r}
#dat_use <- data.frame(rbind(train_dat, vali_dat))
dat_use <- train_dat
glm3 <- glm(fmla_19 , data = dat_use, family ="quasibinomial")

#saveRDS(glm3, file = 'Pred_Model.rds' )
```


## Model equation

```{r}
#summary(glm3)

Vars <- names(glm3$coefficients); Vars[1] <-""
Coefs <- round(glm3$coefficients, 3)

Terms <- rep(NA, length(Vars))

for ( i in 1:length(Vars)){
  Terms[i] <- paste(Vars[i], ' X ', Coefs[i])
}
```

```{r}
pander::pander(summary(glm3)$coefficients, split.table = Inf)
```

## ORs for the predictors

```{r,fig.width = 9, fig.height = 10}
#glm3 <- glm(fmla_19 , data = train_dat, family ="quasibinomial")
sjPlot::sjp.glm(glm3)
```

```{r, results='asis'}
sjPlot::sjt.glm(glm3)
```



## The shapes of the relationship between readmision and age, Length of Stay and Operative time.


```{r}
dat.use <- dat_use[, covs_use]


inv_logit <- function(x){exp(x)/(1+exp(x))}
age_grid <- seq(19, 89, 1)

new_data <- dat.use[ 1:length(age_grid),]
covariate_use <- covs_use
for ( i in covariate_use){new_data[, which(colnames(new_data)==i)] <- new_data[1, which(colnames(new_data)==i)]}
new_data$Age <- age_grid
```


The following three plots display the predictions of a patient with the following profile, as the values of  age, length of stay and operation time change. 


```{r}
rownames(new_data) = NULL
new_data[1, which(colnames(new_data)%in%covariate_use)]
```

### Shape of the effect of age on readmission 

```{r, eval = F}
plot(age_grid, predict(glm3, newdata = new_data, type ="response"), 
    xlab = "Age", ylab ="Risk of readmission", type ="l")
```

```{r ,fig.width = 7, fig.height = 7}
# alternative prediction plot
pp= predict(glm3, newdata = new_data, se.fit=T)
pre <- pp$fit
pre.low <- pp$fit - 1.96*pp$se.fit
pre.high <- pp$fit + 1.96*pp$se.fit


out <- data.frame(Age= age_grid, Pred=inv_logit(pre), pre.low=inv_logit(pre.low), pre.high=inv_logit(pre.high) )

ggplot(out, aes(x=Age)) + 
  geom_line(aes(y=Pred), colour="steelblue") + 
  geom_ribbon(aes(ymin=(pre.low), ymax=(pre.high)), alpha = 0.2, fill ="steelblue" ) +
   labs(x="Age" , y = "Risk of readmission")
```

### Shape of the effect of Length of Stay on readmission

```{r}
los_grid <- seq(0, 60, 0.1)

new_data <- dat.use[ 1:length(los_grid),]

for ( i in covariate_use){new_data[, which(colnames(new_data)==i)] <- new_data[1, which(colnames(new_data)==i)]}
new_data$Length_Of_Stay <- los_grid
#plot(los_grid, predict(glm3, newdata = new_data, type ="response"), 
#     xlab = "Length of Stay", ylab ="Risk of readmission", type ="l")

```

```{r ,fig.width = 7, fig.height = 7}
# alternative prediction plot
pp= predict(glm3, newdata = new_data, se.fit=T)
pre <- pp$fit
pre.low <- pp$fit - 1.96*pp$se.fit
pre.high <- pp$fit + 1.96*pp$se.fit

out <- data.frame(los= los_grid, Pred=inv_logit(pre), pre.low=inv_logit(pre.low), pre.high=inv_logit(pre.high) )

ggplot(out, aes(x=los)) + 
  geom_line(aes(y=Pred), colour="steelblue") + 
  geom_ribbon(aes(ymin=(pre.low), ymax=(pre.high)), alpha = 0.2, fill ="steelblue" ) +
   labs(x="Length of Stay" , y = "Risk of readmission")
```

### Shape of the effect of Operation time on readmission

```{r}
opt_grid <- seq(2, 600, 0.1)

new_data <- dat.use[ 1:length(opt_grid),]
for ( i in covariate_use){new_data[, which(colnames(new_data)==i)] <- new_data[1, which(colnames(new_data)==i)]}
new_data$Operative_Time <- opt_grid

#plot(opt_grid, predict(glm3, newdata = new_data,type = "response"), 
#     xlab = "Operative Time", ylab ="Risk of readmission", type ="l")
```


```{r ,fig.width = 7, fig.height = 7}
# alternative prediction plot
pp= predict(glm3, newdata = new_data, se.fit=T)
pre <- pp$fit
pre.low <- pp$fit - 1.96*pp$se.fit
pre.high <- pp$fit + 1.96*pp$se.fit

out <- data.frame(los= opt_grid, Pred=inv_logit(pre), pre.low=inv_logit(pre.low), pre.high=inv_logit(pre.high) )

ggplot(out, aes(x=los)) + 
  geom_line(aes(y=Pred), colour="steelblue") + 
  geom_ribbon(aes(ymin=(pre.low), ymax=(pre.high)), alpha = 0.2, fill ="steelblue" ) +
   labs(x="Operative Time" , y = "Risk of readmission")
```




# Prediction Table 4

```{r}
new_dat <- dat_nsqip[1:4, match(covs_use, colnames(dat_nsqip))]
```



```{r}
new_dat$Age <- c(55, 60, 60, 60 )
new_dat$SEX <- c("female", "female", "male","male")
new_dat$Elective_Surgery <-  c("Yes", "Yes", "No", "Yes")
new_dat$Disease <- c("Colon_Cancer", "Rectal_Cancer", "DIVERTICULITIS", "ULCERATIVE_COLITIS")
new_dat$Resection <- c("PARTIAL_COLECTOMY", "PROCTECTOMY", "PARTIAL_COLECTOMY", "POUCH")
new_dat$Length_Of_Stay <- c(4, 7, 10, 2)
new_dat$Major_Morbidity <- c("0", "1", "1", "1")
new_dat$Hypertension_On_Medication <- c("No", "No", "Yes", "Yes")
new_dat$DIABETES <- c("NO", "NO", "YES", "YES")
#new_dat$STEROID <- c("No", "No", "No", "No")
new_dat$SMOKing <- c("No", "No", "Yes", "Yes")
new_dat$ASA_Class <- c("1", "1", "3", "3")
new_dat$Operative_Time <- c(100,100, 600, 600)


pred = predict(glm3, new_dat, type = "response") 

tt <- predict(glm3, new_dat, type = "link", se.fit= T) 
low = inv.logit(tt$fit + c(-1.96)*tt$se.fit)
#inv.logit(tt$fit)
up = inv.logit(tt$fit + c(1.96)*tt$se.fit)

out = data.frame(rbind(t(new_dat), 'risk prediction (%)' = round(pred *100, 2),'95% CI' = paste0('[', round(low*100, 2), ", ", round(up*100, 2), "]")) )

colnames(out) <- paste0("Patient", 1:4)
pander::pander(out,  split.table = Inf)
```




